Integrating Social Visual Analysis and Deployment with RCloud

### 2015-03-25 introduction.tex
summarized interviews
backslash
intro and related work

Almost a
half-century ago, Tukey foresaw
much of what is now commonplace in data analysis~\cite{TukeyFDA}.
Powerful, interactive environments for analysis and programming were
the goal, together with an unflinching (and, at the time, somewhat
heretical) insistence in keeping humans as a central part of the
discovery process. His now-famous quip that ``the picture-examining eye is the
best finder we have of the wholly unanticipated'' has come to define
much of visual analytics and exploratory visualization~\cite{TukeyEDA}.

In some way, we have moved far beyond what Tukey imagined:
computing and networking capabilities today far exceed
what was barely imaginable then. 
We argue, on the other hand, that we \emph{develop} our data analysis
solutions, and context in which they become part of the broader issues
being solved in organizations, has not changed as much: the S language
was developed essentially alongside Unix~\cite{TheSSystem}, after all.
In this paper, we turn our attention to this opportunity to use computation
to support, not only individuals, but entire teams and their
work within larger organizations.

@@

This situation can affect how data science teams; as analysts and
toolbuilders, we have experienced this first-hand in our environment, and
others report similar findings. Gutierrez collected interviews with data
scientists~\cite{Gutierrez}, which include the following:

@@

Over the past two years, we prototyped this environment and deployed it in a
production community of data scientists, business analysts and other colleagues.
The platform today has over 300 active accounts; about 20 people use it more
than twice a week, and about 50 people use it more than once a week.  Most of
the active users are members of AT&T Labs, but some others are data scientists
and other collaborators in business units. \gordon{This doesn't measure how
intensely people use it...}

@@

There is much previous work that inspired or influenced ours.
Indeed, many studies have addressed the requirements for future visual
analytics environments.
Previous work that we learned from includes:

{\bf Vistrails} as a landmark prototype of a scientific workflow
and provenance management system. This prototype helped the community
to understand the value of capturing aspects of the processes that
surround data analysis experiments and tools, including detailed
history, collaboration, and deployment.

{\bf iPython notebooks (Jupyter)} are the closest work we are aware of.
The goal of this project is to provide shared notebooks and a remote
execution environment for interpreted scripts. \stephen{Are there 
significant differences involving versioning, provenance, annotation
and other broad process support?}

{\bf RStudio, RShiny} and other packages based on R for creating and
publishing web content such as knitR, Rpubs, rCharts, and gg2v.
These tools are not collaborative, but they are aimed at better
graphics and web applications.

{\bf bl.ocks, jsfiddle, plotly} and other web services for sharing code
and demos.

{ManyEyes} is the best-known original work showing the potential for
integrating data visualization with social media.

Further afield, {\bf Electronic Lab Notebooks} are applications for organizing
and sharing data from scientific lab experiments\cite{Rubacha:2011:ELN}.
In a sense, we hope to adapt and extend this concept to the work of
visual analytics teams.

@@

>>>>

More than a half-century ago, Tukey foresaw
much of what is now commonplace in data analysis~\cite{TukeyFDA}.
Powerful, interactive environments for analysis and programming were
the goal, together with an unflinching (and, at the time, somewhat
heretical) insistence in keeping humans as a central part of the
discovery process. His now-famous quip that ``the picture-examining eye is the
best finder we have of the wholly unanticipated'' has come to define
much of visual analytics and exploratory visualization~\cite{TukeyEDA}.

In some way, we have moved far beyond what Tukey imagined:
computing and networking capabilities today far exceed
what was barely imaginable then. 
We argue, on the other hand, that we \emph{develop} our data analysis
solutions, and context in which they become part of the broader issues
being solved in organizations, has not changed as much: the S language
was developed essentially alongside Unix~\cite{TheSSystem}, after all.
We turn our attention to this opportunity to use computation
to support, not only individuals, but entire teams and their
work within larger organizations. In this paper, we contribute the
design of RCloud, together with an interview study conducted over the
course of its development and deployment at AT\&T Labs, where RCloud has
been in use for about two years.

@@

This situation can affect how data science teams; as analysts and
toolbuilders, we have experienced this first-hand in our environment, and
others report similar findings. Gutierrez collected interviews with data
scientists~\cite{Gutierrez:2014:DSA}, which include the following:

@@

@@

@@

Over the past two years, we prototyped RCloud and deployed it to a
community of data scientists, business analysts and other colleagues.
The platform today has over 300 active accounts; about 20 people use
it regularly, and about 50 people use it more than once a week.  Most of
the active users are members of AT\&T Labs, but some are data scientists
and other collaborators in other business units. \gordon{This doesn't measure how
intensely people use it...}

\carlos{we need a segue into related work}.
